\cleartorecto % A memoir-class command for moving the acknowledgments to a recto page, not verso.
\chapter{Acknowledgements} % For the heading on the page, also registers in the table of contents
\thispagestyle{plain} %This page should have numbers.

I could not have imagined or prepared for the educational or personal opportunities that awaited me in the doctoral program when I joined Columbia. The past five and a half years have allowed me to dive deeply into a topic I love, but I have had my share of highs and lows and I owe a lot to the people I met along the way for helping me make it.

When I at interviewed at Columbia, it was impossible to miss the genuine curiosity and passion for mathematics and science that Professor Arvind Narayanaswamy exudes. It is infectious and reminds me everyday why I signed up for a Ph.D. under him. He always supported me spending time on my own research interests, teaching, and student activities. I have relied on his mentorship from day one, and he will have my gratitude as I move on from his lab.

The support of my labmates-- Karthik, Carlo, Yi, Jeff, Arvind, and many master's and undergraduate students-- has made day to day life in the lab a treat. I am especially thankful to Arvind with whom I have worked since almost the very beginning. I couldn't have made it without his friendship, support, and tolerance for my gabby nature and constant desire to rearrange of furniture. 

My lunch buddies-- Jenny, Emily, and Shu-- have always been there for me when I needed a break from thinking about research. They've never judged me for the (in)frequency of my cooking, and I will miss our daily hour together.

My family-- Mom, Denea, Riana, Luke, and countless others-- has always given me a place to come home to. I do not think you know how much I have valued my time back home.